Deep Learning for Automatic Speech Recognition

### 2015-04-22 Presentation/Presentation.tex
citing

\begin{frame}
	\frametitle{Input Structure of the CNN}
	\includegraphics[scale=0.6, trim=1.1cm 0 0 7.5cm, clip=true]{cnn-input.pdf}

\begin{frame}
	\frametitle{Global Architecture}
	\includegraphics[scale=0.65, trim=2cm 0 0 8cm, clip=true]{cnn-global.pdf}
\end{frame}

@@

\begin{frame}
	\frametitle{A Simpler Example}
	\includegraphics[scale=1, clip=true, trim=5cm 0 0 10cm]{conv-pool.pdf}
\end{frame}

@@

\begin{frame}
	\frametitle{Back-Propagation cont.}
	\includegraphics[scale=0.65, trim=2cm 0 0 8cm, clip=true]{backprop.pdf}
\end{frame}

>>>>

\begin{frame}
	\frametitle{Input Structure of the CNN}
	\includegraphics[scale=0.6, trim=1.1cm 8cm 0 7.5cm, clip=true]{cnn-input.pdf}
	\begin{center}
		\tiny{Credit: Abdel-Hamid et al. 2014}
	\end{center}
\end{frame}

\begin{frame}
	\frametitle{Global Architecture}
	\includegraphics[scale=0.65, trim=2cm 8cm 0 8cm, clip=true]{cnn-global.pdf}
	\begin{center}
		\tiny{Credit: Abdel-Hamid et al. 2014}
	\end{center}
\end{frame}

@@

\begin{frame}
	\frametitle{A Simpler Example}
	\includegraphics[scale=.9, clip=true, trim=5cm 10cm 0 10cm]{conv-pool.pdf}
	\begin{center}
		\tiny{Credit: Abdel-Hamid et al. 2012}
	\end{center}
\end{frame}

@@

\begin{frame}
	\frametitle{Back-Propagation cont.}
	\includegraphics[scale=0.65, trim=2cm 9cm 0cm 8cm, clip=true]{backprop.pdf}
	\begin{center}
		\tiny{Credit: Champandard 2003}
	\end{center}
\end{frame}
